The Unicode Cookbook \linebreak for Linguists

### 2017-12-15 book/chapters/preface.tex
deals with issue #8

This text is meant as a practical guide for linguists, and programmers, who work with data in multilingual computational environments. We introduce the basic concepts needed to understand how writing systems and character encodings function, and how they work together.

@@

Our research uses quantitative methods to compare languages and uncover and clarify their phylogenetic relations. However, the majority of lexical data available from the world's languages is in author- or document-specific orthographies. Having identified and overcome the pitfalls involved in making writing systems and character encodings syntactically and semantically interoperable (to the extent that they can be), we created a suite of open-source Python and R tools to work with languages using profiles that adequately describe their orthographic conventions. Using orthography profiles and these tools allows users to segment text, analyze it, identify errors, and to transform it into different written forms.

We welcome comments and corrections of this text, our source code, and the use case studies that are supplement to this book. Please use the issue tracker or email us directly.

>>>>

This text is meant as a practical guide for linguists, and programmers, who work with data in multilingual computational environments.\footnote{\url{https://github.com/unicode-cookbook/cookbook}} We introduce the basic concepts needed to understand how writing systems and character encodings function, and how they work together.

@@

In our daily working lives, we use quantitative methods to compare languages and uncover and clarify their phylogenetic relations. However, the majority of lexical data available from the world's languages is in author- or document-specific orthographies. Having identified and overcome the pitfalls involved in making writing systems and character encodings syntactically and semantically interoperable (to the extent that they can be), we created a suite of open-source Python and R tools to work with languages using profiles that adequately describe their orthographic conventions. Using orthography profiles and these tools allows users to segment text, analyze it, identify errors, and to transform it into different written forms.

We welcome comments and corrections of this text, our source code, and the use case studies that are supplement to this book.\footnote{\url{https://github.com/unicode-cookbook/recipes}} Please use the issue tracker, email us directly, or find the book on PaperHive, where readers can leave questions and comments.\footnote{\url{https://paperhive.org/}}
